FinalManuscript_DISCS_UG

### 2018-06-24 parts/01_introduction_01contextofstudy.tex
Added title, context of the study, research objectives.

Digital data privacy and security is a growing concern in various fields, such as  \textbf{[insert fields here]}. To meet these needs, various cryptosystems have been developed. A cryptosystem is a system which operates on plaintexts, ciphertexts and keys. a cryptosystem also has an encryption algorithm, which maps a plaintext to a ciphertext, and a decryption algorithm, which maps a ciphertext to a plaintext, given an appropiate key \cite[p.119]{tilborg_encyclopedia_2005}. The encryption and decryption algorithms are chosen such that the plaintext cannot easily be recovered from the ciphertext without knowledge of the key. This allows data to be securely transmitted over a insecure channel:  and thus much research has been done on the development and application of various cryptosystems.

One such particular application of cryptography is image encryption. \cite{arul_murugan_survey_2018}

\textbf{[discuss image encryption briefly, note how main concern is security]}

However, research has also considered a type of cryptosystem, homomorphic cryptosystems, where in addition to allowing the secure transmission of data, it is also possible to perform computations with encrypted data. \cite{fontaine_survey_2007}.

\textbf{[insert brief overview of homomorphic encryption schemes]}.

>>>>

Digital data privacy and security is a growing concern in various fields, such as  cloud computing \cite{potey_homomorphic_2016}, health information systems \cite{kester_cryptographic_2015}, and video surveillance \cite{upmanyu_efficient_2009}. To meet these needs, various cryptosystems have been developed. A cryptosystem is a system which operates on plaintexts, ciphertexts and keys. a cryptosystem also has an encryption algorithm, which maps a plaintext to a ciphertext, and a decryption algorithm, which maps a ciphertext to a plaintext, given an appropiate key \cite[p.119]{tilborg_encyclopedia_2005}. The encryption and decryption algorithms are chosen such that the plaintext cannot easily be recovered from the ciphertext without knowledge of the key. This allows data to be securely transmitted over a insecure channel:  and thus much research has been done on the development and application of various cryptosystems.

One such particular application of cryptography is image encryption. While cryptosystems used to encrypt digital data in general, such as the Advanced Encryption System (AES) or elliptic curve cryptography, can also be used to encrypt images \cite{jain_image_2016, singh_image_2015} other algorithms created specifically for image encryption have also been developed \cite{murugan_survey_2018}.

However, research has also considered a type of cryptosystem, homomorphic cryptosystems, where in addition to allowing the secure transmission of data, it is also possible to perform computations with encrypted data, the most basic of which being addition and multiplication. Numerous homomorphic cryptosystems exist, which allow for data to be manipulated without compromising data privacy \cite{fontaine_survey_2007, sen_homomorphic_2013}. In homomorphic image encryption, there is additional interest in being able to perform image manipulation operations on the encrypted data such as image adjustment, filtering, and morphological/feature extraction operations \cite{ziad_cryptoimg:_2016, gonzalez_digital_2008}.

### 2018-06-24 parts/01_introduction_02researchquestions.tex
Added title, context of the study, research objectives.

This subsection mainly presents your research objective/s in question form. An ideal research question must be open-ended, meaning that there is no clear answer that may be readily given to it. The recommended format for this section is that you provide a single overall question, followed by a series of sub-questions (enumerate them for better readability) that help you in answering your main question.

>>>>

In this study, we ask

### 2018-06-24 parts/01_introduction_03objectives.tex
Added title, context of the study, research objectives.

\section{Research Objectives}
With your context established, it is in this section where you will now describe what you intend to achieve by the end of the study. A possible way of presenting this subsection is to first introduce what problem/s you wish to address given the current context, and based on that/these, you present the objectives that would somehow address that/these problem/s. Other common things discussed may include a brief overview of your intended methodology.

\begin{enumerate}
    \item Research objectives 1...
    \item Research objectives 2...
    \item Research objectives 3...
\end{enumerate}

>>>>

\section{Research Objectives}

A paper published in 2009 by Ziad, et. al. presents \textit{CryptoImg}, a library for the  Open Source Computer Vision Library (OpenCV) which implements various homomorphic encryption and image processing routines using the Paillier homomorphic cryptosystem \cite{ziad_cryptoimg:_2016}. While \textit{CryptoImg} demonstrates that various image manipulation operations are possible in a homomorphic system, we believe this study can be extended by considering other known homomorphic encryption schemes, such as an elliptic curve and ElGamal based cryptosystem presented by Li, et. al. \cite{li_elliptic_2012}, and the fully homomorphic encryption scheme proposed by Smart and Vercauteren \cite{hutchison_fully_2010}. Our study aims to provide an objective comparision of various homomorphic cryptosystems currently in the literature, as they would be used in encrypted image manipulation.
In this study, we wish to
\begin{enumerate}
    \item Compare the applicability of known homomorphic encryption schemes to common image processsing operations, in other words, determine which schemes permit more image processing operations;
		\item Compare the security of common image processsing operations under known homomorphic encryption schemes, using established statistical methods in image encryption;
    \item Compare the efficiency of common image processsing operations under known homomorphic encryption schemes;
    \item Create a plug-in for OpenCV to allow for convenient use of these homomorphic encryption schemes.
\end{enumerate}
